\bibitem{survey}
	Bo Pang and Lillian Lee. “Opinion Mining and Sentiment Analysis.” Found. Trends Inf. Retr., 2(1-2):1–135.

\bibitem{KWM}
	Efthymios Kouloumpis and Theresa Wilson and Johanna Moore. “Twitter Sentiment Analysis: The Good the Bad and the OMG!” The International Conference on Weblogs and Social Media, The AAAI Press, 2011

\bibitem{PP}
	Alexander Pak and Patrick Paroubek. “Twitter as a Corpus for Sentiment Analysis and Opinion Mining.” Proceedings of the Seventh conference on International Language Resources and Evaluation Valletta, Malta, European Language Resources Association (ELRA), 2010

\bibitem{SHA}
	Hassan Saif and Yulan He and Harith Alani. “Semantic Sentiment Analysis of Twitter.” The Semantic Web – ISWC, 2012

\bibitem{S140}
	Alec Go and Richa Bhayani and Lei Huang. “Twitter Sentiment Classification
using Distant Supervision.” Processing, 2009. Sentiment140, http://help.sentiment140.com/home.

\bibitem{Pri}
	Balakrishnan Gokulakrishnan and Pavalanathan Priyanthan and Thiruchittampalam Ragavan and h Prasath and AShehan Perera. “Opinion Mining and Sentiment Analysis on a Twitter Data Stream.” The International Conference on Advances in ICT for Emerging Regions, 2012.

\bibitem{SA}
	Niek Sanders. Twitter Sentiment Corpus. http://www.sananalytics.com

\bibitem{Stem}
	Smirnov, Ilia. “Overview of Stemming Algorithms.” Mechanical Translation, 2008.
http://the-smirnovs.org/info/stemming.pdf.

\bibitem{Porter}
	Porter, Martin. The Porter Stemming Algorithm, 2006. http://tartarus.org/~martin/PorterStemmer/

\bibitem{CMV}
	Councill, Isaac G. and McDonald, Ryan and Velikovich, Leonid. “What's great and what's not: learning to classify the scope of for improved sentiment analysis.” Proceedings of the Workshop on Negation and Speculation in Natural Language (NeSp-NLP '10), p51-59, 2010.

\bibitem{C4.5}
	Quinlan, J. R. C4.5: Programs for Machine Learning, Morgan Kaufmann Publishers, 1993
